### 2011-10-28 doc/manuscript.tex
Just an update.

@@

%=============================================================================
% Table S. 
\begin{table}[!ht]
\caption{
{\bf Virulence genes inferred to have experienced recombining gene transfer
events.}}
\noindent \begin{centering}
\begin{tabular}{lll}
\hline 
Genes & Gene Accessions\tabularnewline
\hline 
putative calcium transporter (MgtA) & SpyM3\_0440 & SPY1 to SDE1\\
putative dipeptidase & SpyM3\_0465 & SPY to SDE\\
superoxide dismutase & SpyM3\_1071 & SPY to SDE\\
putative internalin A precursor & SpyM3\_1035 & SPY to SDE\\
putative heat shock protein (chaperonin GroEL) & SpyM3\_1765 & SPY to SDE1\\
pyruvate formate lyase & SpyM3\_1749 & No specific directions\\
putative glucose kinase & SpyM3\_1180 & SPY to SDE\\
\hline 
\end{tabular}
\par\end{centering}
\label{tab:virrecomb}
\end{table}
%\clearpage{}
%=============================================================================

>>>>

%=============================================================================
% Table S4-1. The significance values of the heat map.
\begin{table}[!ht]
\caption{
{\bf P-values for the significance of the ratios of logarithm base 2 of the observed
recombinant edges to the expected number of recombinant edges.} 
NnN's are for the branch pairs that are impossible under the model-based
approached. Rows are for donor, and columns for recipient.}
\noindent \centering{}\begin{tabular}{cccccccccc}
\hline
&         SDE1&     SDE&    SDE2&      SD&     SDD &ROOT&    SPY1&     SPY&    SPY2\\
\hline
SDE1 &3.1e-03 &    NaN &1.1e-29 &    NaN &8.8e-21  &NaN &4.4e-19 &    NaN &2.2e-23\\
SDE  &4.9e-02 &2.3e-06 &7.5e-04 &    NaN &3.5e-32  &NaN &9.3e-01 &3.0e-08 &1.2e-25\\
SDE2 &8.2e-32 &    NaN &6.0e-01 &    NaN &1.2e-23  &NaN &1.6e-17 &    NaN &3.3e-06\\
SD   &6.4e-11 &8.0e-01 &1.4e-19 &3.2e-02 &7.3e-01  &NaN &2.2e-27 &1.5e-22 &1.1e-30\\
SDD  &7.3e-33 &6.7e-32 &4.1e-04 &    NaN &9.1e-07  &NaN &8.7e-34 &1.8e-32 &8.7e-34\\
ROOT &8.7e-34 &8.7e-34 &8.7e-34 &8.7e-34 &8.7e-34  &NaN &8.7e-34 &8.7e-34 &8.7e-34\\
SPY1 &8.7e-34 &2.9e-32 &8.7e-34 &    NaN &8.7e-34  &NaN &9.3e-01 &    NaN &8.7e-34\\
SPY  &2.6e-13 &2.2e-27 &5.8e-32 &7.5e-01 &8.7e-34  &NaN &1.3e-03 &3.9e-05 &6.5e-02\\
SPY2 &8.7e-34 &2.1e-33 &8.7e-34 &    NaN &8.7e-34  &NaN &9.4e-34 &    NaN &9.3e-01\\
\hline
\end{tabular}
\label{tab:heatmappvalue}
\end{table}

@@

%=============================================================================
% Table S. 
\begin{table}[!ht]
\caption{
{\bf Virulence genes inferred to have experienced recombining gene transfer
events.}}
\noindent \begin{centering}
\begin{tabular}{lrll}
\hline 
Direction & Fraction & Genes & Description\\ 
\hline 
SDE1-to-SDD & 0.97 & SpyM3\_1369 & putative serine threonine kinase\\
 & 0.25 & SpyM3\_1370 & putative phosphoprotein phosphatase\\
SDE2-to-SDD & 1 & SpyM3\_1522 & 3-oxoacyl-acyl carrier protein synthase II\\
 & 1 & SpyM3\_1523 & 3-ketoacyl-acyl-carrier-protein reductase\\
 & 1 & SpyM3\_1524 & acyl-carrier-protein S-malonyltransferase\\
SDD-to-SDE1 & 0.16 & SpyM3\_0499 & F0F1 ATP synthase subunit beta\\
SDD-to-SDE2 & 0.01 & SpyM3\_1767 & putative endopeptidase Clp ATP-binding chain C\\
SDD-to-SDE & 0.49 & SpyM3\_1180 & putative glucose kinase\\
SPY1-to-SDE1 & 0.13 & SpyM3\_0440 & putative calcium transporter\\
SPY1-to-SDE2 & 0.28 & SpyM3\_1755 & putative pyruvate formate-lyase activating enzyme\\
SPY2-to-SDE2 & 0.21 & SpyM3\_0420 & lysyl-tRNA synthetase\\
SPY2-to-SDE & 0.57 & SpyM3\_1806 & DNA mismatch repair protein MutS\\
SDE-to-SDD & 1 & SpyM3\_1188 & phosphopantetheine adenylyltransferase\\
 & 0.31 & SpyM3\_0036 & bifunctional acetaldehyde-CoA alcohol dehydrogenase\\
 & 0.26 & SpyM3\_0499 & F0F1 ATP synthase subunit beta\\
 & 0.05 & SpyM3\_0497 & F0F1 ATP synthase subunit alpha\\
SDE-to-SPY1 & 0.02 & SpyM3\_0440 & putative calcium transporter\\
SDE-to-SPY2 & 0.47 & SpyM3\_1366 & putative two-component response regulator\\
 & 0.19 & SpyM3\_1475 & N-acetylglucosamine-6-phosphate deacetylase\\
 & 0.09 & SpyM3\_1201 & putative two-component sensor histidine kinase\\
 & 0.02 & SpyM3\_1749 & putative pyruvate formate-lyase\\
SDE-to-SPY & 0.58 & SpyM3\_0499 & F0F1 ATP synthase subunit beta\\
 & 0.22 & SpyM3\_0497 & F0F1 ATP synthase subunit alpha\\
 & 0.08 & SpyM3\_1370 & putative phosphoprotein phosphatase\\
SPY-to-SDE1 & 0.86 & SpyM3\_0511 & ABC transporter ATP-binding protein\\
 & 0.18 & SpyM3\_1765 & chaperonin GroEL\\
SPY-to-SPY2 & 0.03 & SpyM3\_1749 & putative pyruvate formate-lyase\\
SPY-to-SDE & 0.98 & SpyM3\_0465 & putative dipeptidase\\
 & 0.84 & SpyM3\_1755 & putative pyruvate formate-lyase activating enzyme\\
 & 0.54 & SpyM3\_1749 & putative pyruvate formate-lyase\\
 & 0.3 & SpyM3\_0764 & putative spermidineputrescine ABC transporter ATP-binding protein\\
 & 0.28 & SpyM3\_0420 & lysyl-tRNA synthetase\\
 & 0.23 & SpyM3\_1182 & putative peroxide resistance protein\\
 & 0.22 & SpyM3\_0440 & putative calcium transporter\\
 & 0.07 & SpyM3\_1366 & putative two-component response regulator\\
 & 0.06 & SpyM3\_1180 & putative glucose kinase\\
\hline 
\end{tabular}
\par\end{centering}
\label{tab:virrecomb}
\end{table}
%\clearpage{}
%=============================================================================
